%-------------------------
% Resume in Latex
% Author : Bilal Khan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
%-------------------------
% Difference:
% - Added Cohere X Opensesame hackathon win -> shortened Vosyn
% - Updated Ericsson description + Updated technologies
% - New Ericsson skills
%
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{mypink3}{cmyk}{0, 0.7808, 0.4429, 0.1412}
\definecolor{cvblue}{HTML}{bf3228}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Muhammad Bilal Khan} \\ \vspace{1pt} Toronto, Ontario, Canada\\ \vspace{2pt}
    \small  \href{mailto:02.mbilalkhan@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{02.mbilalkhan@gmail.com}} ~ \href{tel:+1 647-989-6112}{ \raisebox{-0.1\height}\faPhone\ \underline{+1 647-989-6112} ~}
    \href{https://www.linkedin.com/in/bilal-khan1548/}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{bilal-khan1548}}  ~
    \href{https://github.com/m-bilu}{\raisebox{-0.2\height}\faGithub\ \underline{m-bilu}} ~
    {\raisebox{-0.2\height} \ \href{https://mbilalkhan.vercel.app/}{\textcolor{orange}{\underline{Personal Website}}}
    \vspace{-5pt}
\end{center}

 %-----------EDUCATION-----------
\section{\href{https://github.com/m-bilu/data-set-analysis-coursework}{EDUCATION}}
  \resumeSubHeadingListStart
    \resumeSubheading
    {\href{https://drive.google.com/file/d/1QEfgK4heOBgUVTgv2YxT5KoPsnaf-hhB/view?usp=sharing}{\textcolor{cvblue}{University of Waterloo - Honours Mathematics}}}{06 2020 - 06 2025}{\href{https://github.com/m-bilu/data-set-analysis-coursework}{\underline{Double Major in Statistics, Computational Math, Minor in Optimization}}}

      \resumeItemListStart
        \resumeItem{
        \href{https://github.com/m-bilu/certs}{\textbf{Coursework}: Big Data, Machine Learning, Probability, Discrete Mathematics, Optimization, Data Structures, Algorithms, Operating Systems, Distributed Systems. President's Scholarship: \textbf{\$5000}.
        }}
      \resumeItemListEnd
      \vspace{-5pt}
      
      \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{

    \vspace{-15pt}

    \resumeItem{\textbf{\textcolor{cvblue}{Languages:}}{ Python, C++, Java, JavaScript, TypeScript, SQL, R, Git, Bash, MatLab.}}

    \vspace{-5pt}

    \resumeItem{\textbf{\textcolor{cvblue}{Tools:}}{ Tensorflow, Keras, PyTorch, CUDA, Apache, PostGres, MongoDB, Firebase, Grafana, Prometheus, Loki, AWS, GCP, Azure, React.JS, Node.JS, Flask, FastAPI, Django, Jenkins, Ansible, Docker, Kubernetes, Nginx, CI/CD}
     
    }}}
    
    
    \vspace{0pt}
    
 \end{itemize}
 \vspace{-15pt}



%-----------EXPERIENCE-----------
\section{WORK EXPERIENCES}
  \resumeSubHeadingListStart

   \resumeSubheading
      {\href{https://www.ericsson.com/en}{\textbf{\large{\textcolor{cvblue}{Ericsson}}}} {\medium{}{{\textcolor{cvblue}{}}}} \medium{}}{04 2024 -- Ongoing} 
      {\underline{5G Software Developer Intern, CloudRAN Development Team}}{Kanata, ON, Canada}
      \resumeItemListStart
      \vspace{3pt}

        \resumeItem{Delivered a network monitoring service covering \textbf{15TB} of device metrics; Prometheus/SNMP ETL for real-time metrics collection, visualizing network usage on Grafana. This is automatically scaled using Openshift to cover \textbf{5000} devices.}

        \resumeItem{Leveraged this to develop an \textbf{agentic RAG-based} flow with \textbf{Langchain/Llama3}, automating sub-network reuse to optimize utilization across existing infrastructure, reducing manual hardware ordering/configuration by \textbf{40\%}.}

        
        
        \vspace{1pt}       

        %% Exact tools I have engineered so far, and with what stack. Scope of help (money saved, ppl helped)
        \resumeItem{Developed an \textbf{IaaS} tool which automates hardware ordering, promoting efficient hardware reservation. \textbf{\$1M} projected savings in \textbf{OpEx}. Provided end-to-end solution with system design and ETL pipeline and deployment on \textbf{AWS} EC2.}

        \vspace{1pt}

        %% STAICE
        \resumeItem{Contributed to \textbf{RL}-based Test Channel scheduling, deployment. Deep Q-learning with MDPs, OpenAI PPO, Tensorflow. Replaced manual scheduling workflow, saving \textbf{10 hours per channel deployment}.}

        

        \vspace{1pt}

         

        
        
      \resumeItemListEnd 
      \vspace{3pt}

      \resumeSubheading
          {\href{https://shorturl.at/CNQqc}{\textbf{\large{\textcolor{cvblue}{Department of Statistics, University of Waterloo}}}}\medium{\textcolor{cvblue}{}}}{07 2023 -- 12 2023}
          {\underline{Published Research Assistant}}{Waterloo, ON, Canada}
          \resumeItemListStart
          \vspace{3pt}

          %% General Intro, what did I do
          \resumeItem{Pioneered distributed estimation for diagnostics meta-data-analyses in healthcare with \textcolor{cvblue}{\href{https://uwaterloo.ca/scholar/znegeri/home}{Zelalem Negeri}} \& NSERC's \textbf{\$10,000} grant. Built deep learning algorithm in Python/R for bivariate binomial-normal model.}
          

          %% Technicals
          \resumeItem{Built data scraping, data wrangling pipeline in Python, Kafka to accumlate \textbf{9,000} studies from Cochrane Database. }

          \vspace{1pt}

          %% Impact: So what?
          \resumeItem{Identified relationship between method choice and data characteristics, provided recommendations for method usage and future directions of investigation. Presented paper to \textbf{est. 200} international academics at {\href{https://uwaterloo.ca/joint-research-conference-statistics-quality-industry-technology/}{\textcolor{cvblue}{JRC 2024}}} Student Award.}

          
          \resumeItemListEnd


   \resumeSubheading
      {\href{https://vosyn.ai/}{\textbf{\large{\textcolor{cvblue}{Vosyn}}}} {\medium{}{{\textcolor{cvblue}{}}}} \medium{}}{06 2023 -- 10 2023} 
      {\underline{Machine Learning Engineer}}{Etobicoke, ON, Canada}
      \resumeItemListStart
      \vspace{3pt}


        %% General Intro to MVP for Voice Synth products, Voice Pretrained Transformer, Data Pipelines
        \resumeItem{Developed MVP for multimodal voice synthesis VLM. Implemented CUDA-optimized GPU kernels to accelerate inference by 15\%. Efficient Trained models on local TPU using XLA/MLIR. Presented in funding rounds, evaluated at \textbf{\$36.4M.}}

        %% Collaboration, funding, startup
        \resumeItem{Executed \textbf{60M}-param audio translation model. Established streaming ETL data pipelines for \textbf{10,000} hrs of audio.}

        \vspace{1pt}

        %% Leadership, team stuff
        \resumeItem{Led a subteam of \textbf{7 developers} in a fast-paced startup environment. Subteam grew \textf{200\%} over \textbf{4 months}; Managed Agile environment on Jira, Confluence, Gerrit with custom CI/CD flow; \textbf{20\%} increase in sprint velocity. }
        

        \vspace{1pt}

        %% Literature review required for development - key ML concepts, papers, TTS systems        
        \resumeItem{Implemented literature on open-source TTS systems, transformer architecture, QLora and quantized models for cost-effective LLM training led to a \textbf{20\%} reduction in NVIDIA V100 compute, lowering \textbf{OpEx} by \textbf{\$1000}/month.}

        \vspace{1pt}      

        
        
      \resumeItemListEnd 
            \vspace{-5pt}
    


%-----------PROJECTS-----------
\section{AWARDS \& ACHIEVEMENTS}
\vspace{-5pt}

        \resumeProjectHeading
          {\href{}{}  \medium{\textcolor{cvblue}{}{}}}

          \vspace{-35pt}
           
          \resumeItemListStart

        \resumeItem{\href{https://github.com/Duo-Keyboard-Koalition/Syntaxtual}{\textcolor{cvblue}{\textbf{{1st Place @ Cohere x OpenSesame}}}: Won hackathon by developing Syntaxtual, an LLM-RAG-powered agentic application for live code review in VS Code with repository-level context, allowing for conversational issue resolution.}}

        \vspace{5pt}



        \resumeItem{\href{https://github.com/m-bilu/MAG-WildfireHackathon}{\textcolor{cvblue}{\textbf{{2nd Place @ MAG Aerospace Wildfire Hackathon}}}: Predicted \textbf{10 days} of future fire growth for Alberta's \textbf{Jasper Wildfire} with topography, fire fuel, and fire hotspot raster data. \textbf{Published} in UW Data \& AI Institute 
 {\href{shorturl.at/wdxOb}{\textcolor{cvblue}{Newsletter}}}}.}
        
        \vspace{5pt}

        \resumeItem{\href{https://watai.ca/#/contact}{\textcolor{cvblue}{\textbf{{MedChat @ Waterloo.AI}}}: Built LLM chatbot finetuned on PubMed literature at \textbf{largest undergraduate AI research} hub in Canada. Achieves \textbf{75\%} accuracy on symptoms/diagnosis benchmark with agentic RAG, Llama 3.}}

        \vspace{5pt}

        \resumeItem{\href{https://www.uoft.ai/projectx}{\textcolor{cvblue}{\textbf{{ProjectX @ UofT AI}}}: Representing UWaterloo at 3 month research hackathon on multimodal co-learning, data fusion. Focusing on multi-messenger models for neutrino detection. Submission paper also awaiting journal publishing.}}
        
        \vspace{5pt} 


        \resumeItem{\href{https://globalspark.world/}{\textcolor{cvblue}{\textbf{{Lead Developer @ Global Spark, BCG}}}: Developed NLP-based ATS system for HackTheGlobe applications by finetuning Cohere R7B with AutoML and dataset generation. Hosting workshops on LLMs, Computer Vision, mentoring.}}
        
        \vspace{5pt} 

        
          \resumeItemListEnd 
         \vspace{-12pt}


    \vspace{-5pt}
  




\end{document}
